\section{Setup}

Before reporting our results, we first describe the benchmarks and models we consider in our experiments and describe our evaluation procedure.

\subsection{Benchmarks}
In our experiments, we consider five NLI benchmarks, we describe them briefly below, a more elaborate description can be found in \cref{app:benchmarks}. 
% : ANLI \citep{nie-etal-2020-adversarial}, HANS \citep{mccoy-etal-2019-right}, MNLI \citep{williams-etal-2018-broad}, SNLI \citep{bowman-etal-2015-large}, and $\alpha$NLI \citep{bhagavatula2020abductive}, also known as abductiveNLI.
% We briefly discuss each of these benchmarks below.

\vspace{-1mm}
\paragraph{SNLI}
The first and most bencrhmark we consider is the Stanford Natural Language Inference (SNLI), one of the first large-scale NLI datasets for NLP evaluation, sourced via Amazon Mechanical Turk.
We use the dev set of the corpus, which comprises 10K examples.

\vspace{-1mm}
\paragraph{MNLI}
The Multi-Genre NLI (MNLI) corpus \citep{williams-etal-2018-broad} was introduced as an alternative to SNLI that captures more genres and more challenging examples. 
Also for MNLI, we consider the around 10K examples dev set of the corpus.

\vspace{-1mm}
\paragraph{HANS}
The adversarial dataset Heuristic Analysis for NLI Systems \citep[HANS,][]{mccoy-etal-2019-right}.
The dataset is generated to contain examples that cannot be solved through heuristics like lexical overlap, and contains 30K examples.

\vspace{-1mm}
\paragraph{ANLI}
The second adversarial dataset we consider is Adversarial NLI, or ANLI \citep{nie-etal-2020-adversarial}.
The dataset, created with the primary aim to make SOTA models fail, is sourced iteratively in a human-in-the-loop setup.
In our experiments, we consider the dev set of iteration 3, the most challenging set of the benchmark.

\vspace{-1mm}
\paragraph{$\alpha$NLI}
$\alpha$NLI or abductive NLI \citep{bhagavatula2020abductive} has a different setup than the previous benchmarks, focusing specifically on \emph{abductive reasoning}..
Each sample consist of a pair of observations at two consecutive times, a plausible hypothesis that explains tho two observations, and an implausible hypothesis that does not (or to a lesser extent).
The task is to select the most plausible hypothesis.
The dataset contains 1500 examples.

\vspace{-1mm}
\paragraph{ChaosNLI}
Lastly, we consider the dataset ChaosNLI \citep{nie-etal-2020-learn}.
ChaosNLI contains 100 additional (human) labels for 1500 examples of SNLI, MNLI and $\alpha$NLI, respectively.

\subsection{Models} For each of these benchmarks, we compute and analyse scores for two different model families: Llama \citep{dubey2024llama} and Mistral \citep{jiang2023mistral, jiang2024mixtral}. 
Specifically, we use Meta-Llama 3.1 \{8, 70, 405\}B from the Llama series, and Mistral 7B / Mixtral 8x\{7, 22\}B from the Mistral series.
We limit our analysis to pre-trained base models and leave the analysis on post-trained / instruct models to future work.
% The model sizes range from 2B to 405B in our analysis.

\subsection{Evaluation details}
As nowadays common for pre-trained models, we consider the choice-based evaluation setup for all the tasks rather than generative. 
In this setup, the model is presented with the few shot examples (if present) along with the question and the available choices in a multiple choice set-up, and is then asked to predict the correct letter choice.
% like \textit{A: Entailment}, \textit{B: Neutral}, and \textit{C: Contradiction}, and then asked to predict the correct letter choice. 
Since there are only a limited number of choices depending on the task (two or three), we append the these choices to the prompt and compute the negative log likelihood (NLL) over the letter choice. 
We then choose the option which has the lowest NLL as the model's prediction. 
The prompt templates for all tasks are detailed in Table \ref{tab:prompt_template}.


% \dieuwke{Temperature setting?}
% \dieuwke{I think it may be nice to add something already about what we compute and to what end.}
% \dieuwke{SHould perhaps mention our baselines as well?}
